\documentclass[letterpaper, 12pt]{article}
\usepackage[top=0in, bottom=-.1in, left=0in, right=0in]{geometry}

\newbox\boxfront
\newbox\boxback
\newbox\boxlastfront
\newbox\boxa
\newbox\boxb
\newbox\boxc
\newbox\boxd
\newbox\boxe
\newbox\boxf
\newbox\boxg
\newbox\boxh

\count10 = 0%

\begin{document}%
\newcommand{\flashcardfront}[4]{%
\hbox to 4.25in{%
\hskip 0.25in%
\vbox to 2.75in{%
\vskip 0.25in%
\hbox to 3.75in{\small#1\hss#2}%
\vskip 0.25in%
\hbox to 3.75in{\hfill \mbox{\LARGE #3}\hfill}%
\vss%
\hbox to 3.75in{\hfill \parbox{3.75in}{#4\hfill}\hfill}%
\vss%
\vskip 0.25in%
}%
}%
}%
\newcommand{\flashcardback}[4]{%
\hbox to 4.25in{%
\hskip 0.25in%
\vbox to 2.75in{%
\vskip 0.25in%
\hbox to 3.75in{\hfill\parbox{3.75in}{#1\hfill}\hfill}%
\vss%
\hbox to 3.75in{\hfill\parbox{3.75in}{Garnish: #2\hfill}\hfill}%
\vss%
\hbox to 3.75in{\hfill\parbox{3.75in}{Instructions: #3\hfill}\hfill}%
\vss%
\hbox to 3.75in{\small\hfill Source: #4}%
\vskip 0.25in%
}%
}%
}%
\newcommand{\flashcard}[8]{%
\setbox\boxfront\vbox{\flashcardfront{#1}{#2}{#3}{#4}}%
\setbox\boxback\vbox{\flashcardback{#5}{#6}{#7}{#8}}%
\ifnum\count10 = 0%
\setbox\boxlastfront\box\boxfront%
\setbox\boxa\box\boxback%
\else%
\ifnum\count10 = 1%
\hbox{\box\boxlastfront\box\boxfront}%
\setbox\boxb\box\boxback%
\else%
\ifnum\count10 = 2%
\setbox\boxlastfront\box\boxfront%
\setbox\boxc\box\boxback%
\else%
\ifnum\count10 = 3%
\hbox{\box\boxlastfront\box\boxfront}%
\setbox\boxd\box\boxback%
\else%
\ifnum\count10 = 4%
\setbox\boxlastfront\box\boxfront%
\setbox\boxe\box\boxback%
\else%
\ifnum\count10 = 5%
\hbox{\box\boxlastfront\box\boxfront}%
\setbox\boxf\box\boxback%
\else%
\ifnum\count10 = 6%
\setbox\boxlastfront\box\boxfront%
\setbox\boxg\box\boxback%
\else%
\ifnum\count10 = 7%
\hbox{\box\boxlastfront\box\boxfront}%
\setbox\boxh\box\boxback%
\hbox{\box\boxb\box\boxa}%
\hbox{\box\boxd\box\boxc}%
\hbox{\box\boxf\box\boxe}%
\hbox{\box\boxh\box\boxg}%
\count10 = -1%
\fi%
\fi%
\fi%
\fi%
\fi%
\fi%
\fi%
\fi%
\advance\count10 by 1%
}%
\flashcard{}{House Special}{Ex Boyfriend}{%
You're pretty sure it's over, but you keep coming back for more.
}{%
1 oz. gin

1 oz. grapefruit juice

1/2 oz. ginger liqueur

2 dashes Angustura bitters
}{%
none
}{%
Shake with ice in a mason jar and serve directly.
}{Sarah Georg}%
\flashcard{}{House Special}{Eastern Substitution}{%
I guess this is what you do when you run out of lemon juice.  It looks like a swirling brown mess though.
}{%
1 oz. amaretto

1 oz. tamarind juice

1/2 oz. simple syrup
}{%
none
}{%
shake with ice and strain into chilled sour glass.
}{Manfred Georg}%
\flashcard{}{House Special}{Bucking Jesus}{%
Oh, how we miss you, El Bronco.  This is our completely inauthentic tribute.
}{%
1 oz. Light Rum (wasn't it vodka?)

1 oz. tamarind juice

1 oz. simple syrup

pinch chili powder
}{%
chili powder
}{%
Rim cocktail glass with chili powder.  Shake with ice and strain into glass.
}{Sarah and Manfred Georg}%
\flashcard{4/5}{Traditional Cocktail}{Old Fashioned}{Whiskey with some sweetness and aroma added.  The original cocktail.}{%
2 oz. rye or bourbon whiskey

1/4 oz. simple syrup

2 dashes Angostura bitters}{lemon twist}{Build in old fashioned glass.}{Mr. Boston page 26}%
\flashcard{}{Traditional Cocktail}{Tuxedo Cocktail}{%
Only traditional spirits make this surprising and surprisingly old cocktail.
}{%
1 oz. old tom gin

1 oz. dry vermouth

1 tsp. absinthe

1 tsp. maraschino liqueur

2 dashes orange bitters
}{%
Maraschino cherry
}{%
Stir with ice and strain into chilled cocktail glass.  Garnish.
}{Mr. Boston page 104}%
\flashcard{3/5}{Traditional Cocktail}{Manhattan}{Whiskey with some sweetness and spice.  One of the first cocktails.  A little more complex than an old fashioned.}{%
2 oz. rye whiskey

1/2 oz. sweet vermouth

1 dashes Angostura bitters}{Maraschino cherry}{Stir with ice and strain into chilled cocktail glass.  Garnish with cherry.}{Mr. Boston page 28}%
\flashcard{2/5}{Traditional Cocktail}{Traditional Martini}{%
The first martini were a mixture of gin and vermouth (sweet or dry).  A much better combination than today's shot of gin or vodka with an olive.}{%
1 oz. gin

1 oz. vermouth (sweet or dry)

1 dash orange bitters
}{%
lemon twist}{%
Stir with ice and strain into a cocktail glass.  Add lemon twist.}{Mr. Boston page 32}%
\flashcard{}{Traditional Cocktail}{Negroni}{%
Bitter, floral, complex.  No cocktail can claim to be more Italian.
}{%
3/4 oz. gin

3/4 oz. Campari

3/4 oz. sweet vermouth
}{%
orange twist
}{%
Stir with ice and strain into cocktail chilled glass. Garnish.
}{Mr. Boston page 92}%
\flashcard{}{Traditional Cocktail}{Tom Collins}{%
Named for a hilarious joke.  A sour gin soda.
}{%
2 oz. gin

1 oz. lemon juice

1 oz. simple syrup

soda water
}{%
orange and lemon wheel and maraschino cherry
}{%
shake with ice and strain into collins glass.  Add ice and soda, stir and garnish.
}{Mr. Boston page 103}%
\flashcard{4/5}{}{The Sfozando}{%
Incredibly complex flavors, starting with a sharp mezcal smokiness moving through an herbal spiciness and ending in semi-sweet chocolate.
}{%
1 oz. mezcal

3/4 oz. rye whiskey

1/2 oz. dry vermouth

1/2 oz. benedictine

1 dash chocolate bitters
}{%
orange twist
}{%
Stir with ice and strain into cocktail glass.  Garnish.
}{Mr. Boston page 146}%
\flashcard{3/5}{}{The Interesting Cocktail}{%
This cocktail is, well, interesting.
}{%
2 oz. blanco tequila

1/2 oz. Aperol

1/2 oz. dark cr\`eme de cacao

3/4 oz. lemon juice
}{%
grapefruit twist
}{%
shake with ice and strain into cocktail glass.
}{Mr. Boston page 141}%
\flashcard{}{}{Mercy, Mercy}{%
Strong with a little sweetness from the bitter aperol.
}{%
2 oz. gin

1/2 oz. Aperol

1/2 oz. Lillet Blanc

1 dash Angustura bitters
}{%
orange twist
}{%
Stir with ice and strain into cocktail chilled glass. Garnish.
}{Mr. Boston page 91}%
\flashcard{}{}{Purple Passion Iced Tea}{%
An alternative to the long island iced tea.  Just as strong.
}{%
1/2 oz. each of vodka, light rum, gin, black raspberry liqueur, simple syrup

3/4 oz. lemon juice

3 oz. lemon lime soda
}{%
lemon twist
}{%
Pour in order into ice filled highball glass. Garnish.
}{Mr. Boston page 168}%
\flashcard{}{}{Mr. 404}{%
Like a flower arrangement in a grapefruit.
}{%
1 1/2 oz. vodka

3/4 oz. elderflower liqueur

3/4 oz. lemon juice

1/2 oz. simple syrup

1/2 oz. Aperol
}{%
orange twist
}{%
shake with ice and strain into chilled cocktail glass.
}{Mr. Boston page 166}%
\flashcard{5/5}{Post War Era Cocktail}{Margarita}{%
The reigning champion of sours.  Tequila, orange liqueur, and lime juice.  Perfect.
}{%
1 1/2 oz. blanco tequila

3/4 oz. Contreau or triple sec

3/4 oz. fresh lime juice
}{%
lime wedge
}{%
Rim chilled cocktail glass with lime wedge and salt.  Shake ingredients with ice and strain into glass.  Add lime wedge.
}{Mr. Boston page 36}%
\flashcard{}{Prohibition Era Cocktail}{Daiquiri}{%
Perhaps the simplest example of a sour.  If you like a pure experience, this is the drink for you.
}{%
2 oz. light rum

3/4 oz. fresh lime juice

3/4 oz. simple syrup
}{%
none
}{%
Shake with ice and strain into a chilled cocktail glass.
}{Mr. Boston page 37}%
\flashcard{3/5}{Prohibition Era Cocktail}{Sidecar}{%
A sour with some character.  Brandy or Cognac, orange liqueur, and lemon juice.  Definitely a lot going on, but the brandy still shines through.
}{%
1 oz. Cognac

1 oz. triple sec

1/2 oz. lemon juice
}{%
none
}{%
Shake with ice and strain into a chilled cocktail glass.
}{Mr. Boston page 37}%
\flashcard{5/5}{Prohibition Era Cocktail}{Bee's Knees}{%
Citrus and juniper with a smooth honey sweet.
}{%
2 oz. gin

1/2 oz. lemon juice

3/4 oz. honey syrup
}{%
none
}{%
Shake with ice and strain into a chilled champagne coupe.
}{Mr. Boston page 69}%
\flashcard{5/5}{Created by Sam Ross in 2005}{Penicillin}{%
Robust oak and ginger flavor with a smoky aroma and just enough sweetness to take the edge off.  Seriously complex.
}{%
1 3/4 oz. Scotch whisky

3/4 oz. lemon juice

1/2 oz. honey syrup

1/2 oz. ginger liqueur

1/4 oz. smoky Scotch whisky
}{%
lemon wheel
}{%
Shake first four ingredients with ice and strain into ice filled old fashioned glass.  Float smoky Scotch on top and garnish with lemon.
}{Mr. Boston page 197}%
\flashcard{5/5}{}{Fitzgerald}{%
Lemon and gin in a perfectly sweet combination.  Quite possibly the best sour there is.
}{%
1 1/2 oz. gin

1 oz. simple syrup

3/4 oz. lemon juice

2 dash Angostura bitters
}{%
lemon wedge
}{%
Shake with ice and strain into a chilled old fashioned glass.  Garnish with lemon.
}{Mr. Boston page 80}%
\flashcard{5/5}{}{Bitter Elder}{%
Tastes remarkably like grapfruit juice, particularly considering there isn't any in it.
}{%
1 1/2 oz. gin

3/4 oz. Elderflower liqueur

3/4 oz. Campari

1/2 oz. lemon juice
}{%
none
}{%
Shake with ice and strain into a chilled cocktail glass.
}{http://www.makemeacocktail.com/}%
\flashcard{3/5}{}{Long Island Iced Tea}{%
A dangerously strong drink that tastes surprisingly like sweet iced tea.
}{%
3/4 oz. vodka, blanco tequila, gin, light rum, triple sec

1/2 oz. simple syrup, lemon juice

Cola
}{%
lemon wedge
}{%
Shake non-cola ingredients with ice and pour, with ice, into highball glass.  Add cola for color.  Add lemon.
}{Mr. Boston page 165}%
\flashcard{3/5}{}{Chapala}{%
A citrusy and refreshing tequila based drink.
}{%
1 1/2 oz. reposado tequila

1 1/2 oz. fresh orange juice

3/4 oz. lemon juice

1/4 oz. grenadine
}{%
Orange blossoms (optional) and orange wedge
}{%
Shake and strain into hurricane glass.  Add crushed ice.  Garnish.
}{Mr. Boston page 138}%
\flashcard{5/5}{}{High Plains Drifter \#1}{%
A delicious, flavorful concoction somewhat similar to a margarita but with much more character.
}{%
2 oz. blanco tequila

3/4 oz. fresh lime juice

3/4 oz. honey syrup

1 dash Angostura bitters

1 splash Campari (coat glass)
}{%
none
}{%
Shake with ice and strain into chilled, Campari coated cocktail glass.
}{Mr. Boston page 141}%
\flashcard{}{}{Nicky Finn}{%
Some complexity mixed with orange and sour.
}{%
1 oz. brandy

1 oz. triple sec

1 oz. lemon juice

1 dash pastis or absinthe
}{%
maraschino cherry or lemon twist
}{%
Shake with ice and strain into chilled cocktail glass.  Garnish.
}{Mr. Boston page 59}%
\flashcard{4/5}{}{Lumination}{%
Ginger-lemon with a little complexity to balance it out.
}{%
2 slices ginger

1 oz. simple syrup

2 oz. dark rum

1 oz. VS Cognac

1 oz. lemon juice

1 dash Angustura bitters
}{%
lemon twist
}{%
Muddle Ginger in syrup.
Shake with ice and strain into chilled champagne flute.
Garnish
}{Mr. Boston page 124}%
\flashcard{5/5}{}{Cable Car}{%
Sweet vanilla, orange, and cinnamon.  Delicious.
}{%
2 oz. spiced rum

3/4 oz. triple sec

3/4 oz. lemon juice

1/2 oz. simple syrup
}{%
cinnamon/sugar rim, lemon wedge, lemon twist
}{%
Rim cocktail glass.
Shake with ice and strain into cocktail glass.
Garnish
}{Mr. Boston page 113}%
% Champagne Cocktails
\flashcard{}{Champagne Cocktail}{Redhead Martini}{%
Strawberry citrus with some bubbly champagne.
}{%
4 strawberries

3/4 oz. lemon juice

3/4 oz. simple syrup

1 1/2 oz. citrus-flavored vodka

1 splash moscato d'Asti or sweet sparkling wine
}{%
strawberry
}{%
Muddle strawberries with lemon juice and syrup.  Add vodka and ice and shake.  Strain into chilled cocktail glass.  Add champagne and garnish.
}{Mr. Boston page 168}%
\flashcard{5/5}{Champagne Cocktail}{Rosemary Clementine Sparkle}{%
Citrus with some complexity from honey and rosemary.
}{%
1/4 clementine or mandarin orange

1 1/2 oz. vodka

3/4 oz. lemon juice and 3/4 oz. honey syrup

1 rosemary sprig

1 splash champagne
}{%
1 rosemary sprig
}{%
squeeze clementine into mixing glass and add rind.  Add other ingredients and shake with ice.  Strain into cocktail glass.  Add champagne and garnish.
}{Mr. Boston page 169}%
\flashcard{}{Champagne Cocktail}{Le Paradini}{%
Berry, fruit, sparkle, awesome!
}{%
1 1/2 oz. vodka

1/2 oz. raspberry liqueur

1/2 oz. Grand Marnier

1 oz. chilled champagne
}{%
none
}{%
Shake first three ingredients with ice and strain into chilled cocktail glass.  Add champagne.
}{Mr. Boston page 164}%
\flashcard{}{Champagne Cocktail}{The Big Crush}{%
Raspberry, orange and champagne deliciousness.
}{%
1 oz. raspberry vodka

1/2 oz. triple sec

1/2 oz. raspberry liqueur

1/2 oz. fresh lime juice

chilled champagne
}{%
blackberry/raspberry
}{%
Shake with ice and strain into cocktail glass.  Top with champagne and garnish.
}{Mr. Boston page 155}%
\flashcard{}{Champagne Cocktail}{Apple-Cinnamon Sparkler}{%
Exactly as the name implies.  However, it tastes more extravagant than it sounds.
}{%
1 oz. apple cider

1/2 oz. cinnamon syrup

1/4 oz. lemon juice

4 oz. sparkling wine or champagne
}{%
Red apple slice
}{%
Gently fold ingredients in mixing glass with ice.  Strain into chilled champagne flute.  Top with splash of champagne and garnish.
}{Mr. Boston page 283}%
\flashcard{}{Champagne Cocktail}{Bellini}{%
Peach and prosecco.  It's like a peach mimosa.
}{%
1 oz. peach puree

5 oz. chilled prosecco
}{%
none
}{%
Pouch puree into chilled champagne flute.  Add prosecco carefully.
}{Mr. Boston page 283}%
\flashcard{}{Champagne Cocktail}{Berry Fizz}{%
Fruity and floral.  A complicated fizz.
}{%
2 (black)berries

3/4 oz. lemon juice

3/4 oz. simple syrup

1 oz. Lillet Blanc and 1 oz. gin

2 oz. chilled sparkling wine
}{%
(black)berries
}{%
Muddle berries with lemon and syrup.  Shake with ice and strain into chilled champagne flute. Top with sparkling wine and garnish.
}{Mr. Boston page 284}%
\flashcard{}{Champagne Cocktail}{The Champagne Cocktail}{%
Despite its name, it isn't just champagne.  Note: substitute an orange twist for the lemon twist and you have a ``London Special.''
}{%
1 sugar cube

2 dashes Angostura bitters

champagne
}{%
lemon twist
}{%
Place sugar and bitters in champagne flute.  Fill with champagne.  Garnish.
}{Mr. Boston page 285}%
\flashcard{}{Champagne Cocktail}{Cranberry Spiced Champagne}{%
Just like grandma used to make for Thanksgiving.
}{%
6 fresh cranberries

1/4 oz. lemon juice

1 tsp. agave nectar

1 pinch pumpkin pie spice

4 oz. sparkling wine or champagne
}{%
3 fresh cranberries
}{%
Muddle. Add champagne and ice and gently fold.  Strain into chilled flute and top with champagne splash.  Float 3 cranberries.
}{Mr. Boston page 286}%
\flashcard{}{Champagne Cocktail}{Death in the Afternoon}{%
You like anise, so this cocktail is perfect for you.
}{%
1 oz. absinthe or pastis

5 oz. chilled champagne
}{%
none
}{%
Pour pastis into champagne flute.  Top with champagne.
}{Mr. Boston page 286}%
\flashcard{2/5}{Champagne Cocktail}{Kir Royale}{%
Simple but perfect.  Who would have thought currants were so good?
}{%
5 1/2 oz. champagne

1/2 oz. cr\`eme de cassis
}{%
none
}{%
Pour into champagne flute (or white wine glass).
}{Mr. Boston page 288}%
\flashcard{1/5}{Champagne Cocktail}{Mimosa}{%
A cocktail which basically screams out brunch.
}{%
1 oz. fresh orange juice

5 oz. champagne
}{%
orange half wheel
}{%
Pour juice into chilled champagne flute.  Add champagne carefully.  Garnish.
}{Mr. Boston page 288}%
\flashcard{}{Champagne Cocktail}{Strawberry-Vanilla Sparkler}{%
The name really says it all.
}{%
1 strawberry (sliced)

1/4 oz. simple syrup

1/4 oz. lemon juice

1/2 oz. vanilla liqueur

4 oz. sparkling wine or champagne
}{%
Strawberry slice
}{%
Muddle berry, syrup and lemon.  Add remaining ingredients and fold with ice.  Strain into champagne flute.  Top with splash of champagne and garnish.
}{Mr. Boston page 291}%
\flashcard{}{Champagne Cocktail}{Luxury Cocktail}{%
Brandy spiked champagne is a true luxury.  Satisfaction guaranteed (or return the drink for a full refund).
}{%
1 oz. brandy

2 dashes orange bitters

3 oz. champagne
}{%
none
}{%
Gently fold ingredients with ice.  Strain into champagne flute.
}{Mr. Boston page 58}%
\flashcard{5/5}{Champagne Cocktail}{French 75}{%
Packs a serious punch.  Gin and champagne is not to be trifled with lightly.
}{%
1 1/2 oz. gin

3/4 oz. lemon juice

1/2 oz. simple syrup

champagne
}{%
none
}{%
Shake first three ingredients with ice.  Strain into chilled champagne flute and top with champagne.
}{Mr. Boston page 80}%
\flashcard{}{Champagne Cocktail}{The Holy Roller}{%
Mint, honey, bitters, citrus.  Holy Roller!
}{%
1 1/2 oz. cacha\c{c}a (Brazilian rum)

3/4 oz. fresh lime juice

1/2 oz. honey syrup

6-8 fresh mint leaves

2 dashes Angostura bitters

1/2 oz. champagne or sparkling wine
}{%
fresh mint sprig
}{%
Shake non-champagne ingredients with ice.  Strain into cocktail glass.  Add champagne and garnish.
}{Mr. Boston page 121}%
\flashcard{}{Champagne Cocktail}{The Old Cuban}{%
Mint, rum, and champagne in a well balanced combination.
}{%
6 fresh mint leaves

1 oz. simple syrup

3/4 oz. fresh lime juice

1 1/2 oz. dark rum

2 dashes Angostura bitters

2 oz. champagne
}{%
chopped fresh mint
}{%
Muddle mint syrup and lime juice.  Add rum bitters and ice and shake.  Strain into chilled cocktail glass.  Add champagne and garnish.
}{Mr. Boston page 126}%
\flashcard{}{Champagne Cocktail}{Scotch Royale}{%
A champagne cocktail for the whisky lover.
}{%
1 sugar cube

1 dash Angostura bitters

1 1/2 oz. blended Scotch whisky

chilled champagne
}{%
none
}{%
Place sugar and bitters in chilled champagne flute.  Stir Scotch with ice in mixing glass and strain into flute.  Fill with champagne.
}{Mr. Boston page 201}%
\flashcard{}{Champagne Cocktail}{The Seelbach Cocktail}{%
A more appropriate name would be ``Slapped upside the Face with Bitters.''  
}{%
3/4 oz. bourbon whiskey

1/2 oz. triple sec

7 dashes Angostura bitters

7 dashes Peychaud's bitters

4 oz. chilled champagne
}{%
orange twist
}{%
Add in order given to chilled champagne flute.  Garnish.
}{Mr. Boston page 202}%
\flashcard{}{Champagne Cocktail}{Arise My Love}{%
Mint and champagne.  I guess that goes together.
}{%
1 tsp. green cr\`eme de mente

Chilled champagne
}{%
none
}{%
Add (in order) to champagne flute.
}{Mr. Boston page 211}%
\flashcard{}{Champagne Cocktail}{The Oscar Wilde}{%
You better know what you're getting into.
}{%
1 1/4 oz. absinthe

3/4 oz. lemon juice

3/4 oz. simple syrup

1 egg white

1 oz. chilled champagne
}{%
freshly grated nutmeg and orange twist
}{%
Shake first four ingredients without ice.  Add ice and shake again.  Strain into white wine glass.  Top with champagne.  Sprinkle with nutmeg and add orange twist.
}{Mr. Boston page 217}%
\flashcard{}{Champagne Cocktail}{Ritz Fizz}{%
Champagne with a hint of citrus and almond.
}{%
1 dash lemon juice

1 dash blue cura\c{c}ao

1 dash amaretto

chilled champagne
}{%
lemon twist
}{%
Add first three ingredients to champagne flute.  Add champagne.  Garnish.
}{Mr. Boston page 219}%
% Alcohol Free
\flashcard{5/5}{Alcohol Free}{Berry Soda}{%
Muddled berries with honey and ginger.  Very delicious.
}{%
4 blackberries (or Raspberries)

1 oz. honey syrup

1/2 oz. lemon juice

5 oz ginger ale
}{%
blackberry and lemon wheel
}{%
Muddle berries with honey and lemon juice.  Add ice and shake.  Strain into ice filled pilsner glass.  Top with ginger ale and stir briefly.  Garnish.
}{Mr. Boston page 294}%
\flashcard{}{Alcohol Free}{Raspberry lemonade}{%
A Raspberry and lemon soda.
}{%
1 oz. lemon juice

1 oz. raspberry syrup

1/2 oz. simple syrup

Soda water or plain water
}{%
none
}{%
Stir first three ingredients in collins glass. Add ice, fill with water, and stir again.
}{Mr. Boston page 298}%
\flashcard{4/5}{Alcohol Free}{Lime Cooler}{%
A real tonic.
}{%
1/2 oz. fresh lime juice

tonic water
}{%
Lime wedge
}{%
Add juice to ice filled collins glass.  Fill with tonic water and stir.  Garnish.
}{Mr. Boston page 298}%
\flashcard{1/5}{Alcohol Free}{Orange and Tonic}{%
Simple but good: orange juice and tonic water.
}{%
3 oz. fresh orange juice

4 oz. tonic water
}{%
Lime wedge
}{%
Add juice to ice filled collins glass.  Fill with tonic water and stir.  Garnish.
}{Mr. Boston page 298}%
\flashcard{}{Alcohol Free}{Pomegranate Almond Soda}{%
Pomegranate and almond, a perfect combination.
}{%
1 oz. pomegranate juice

1 oz. almond or orgeat syrup

5 oz. soda water
}{%
lime wedge
}{%
Pour into ice filled pilsner glass and stir briefly.  Add lime.
}{Mr. Boston page 299}%
\flashcard{}{Alcohol Free}{Pineapple Mint Soda}{%
Pineapple and mint.  Tart and sweet with great aroma.
}{%
2 oz. pineapple juice

3/4 oz. fresh lime juice

1 oz. demerara syrup

4 oz. soda water
}{%
fresh mint sprigs
}{%
Shake first three ingredients with ice and strain into ice filled pilsner glass.  Top with soda water and stir briefly.  Garnish.
}{Mr. Boston page 299}%
\flashcard{}{Alcohol Almost Free}{Rumless Rickey}{%
Tart, sweet, and complex.  One of the best.
}{%
1 oz. fresh lime juice

1 tsp. grenadine

1 dash Angostura bitters (contains alcohol)

4 oz. soda water
}{%
long lime twist
}{%
Add juice, grenadine, and bitters to ice filled old fashioned glass.  Fill with soda water and stir.  Garnish.
}{Mr. Boston page 300}%
% Extras for alignment and padding.
\flashcard{}{Cocktail}{Something}{%
Snarky remarks.
}{%
1 something

1 oz. something else
}{%
garnish
}{%
instructions
}{page number}%
\flashcard{}{Cocktail}{Something}{%
Snarky remarks.
}{%
1 something

1 oz. something else
}{%
garnish
}{%
instructions
}{page number}%
\flashcard{}{Cocktail}{Something}{%
Snarky remarks.
}{%
1 something

1 oz. something else
}{%
garnish
}{%
instructions
}{page number}%
\flashcard{}{Cocktail}{Something}{%
Snarky remarks.
}{%
1 something

1 oz. something else
}{%
garnish
}{%
instructions
}{page number}%
\flashcard{}{Cocktail}{Something}{%
Snarky remarks.
}{%
1 something

1 oz. something else
}{%
garnish
}{%
instructions
}{page number}%
\flashcard{}{second to last}{second to last}{%
second to last.
}{%
second to last
}{%
second to last
}{%
second to last
}{second to last}%
\flashcard{}{Last}{Last}{%
Last
}{%
Last
}{%
Last
}{%
Last
}{Last}%
%
%
%
%
%
%
%
% Company B 138
% 
\end{document}
